Informing forest carbon inventories under the Paris Agreement using the Global Forest Carbon Database (ForC v4.0)

### 2023-06-09 doc/manuscript/ForC-EFDB manuscript for ESSD.Rmd
refine data statement

bibliography: references.bib
running:
  title: Informing forest CO~2~ inventories with ForC
  author: Anderson-Teixeira et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: |
### The author's copyright for this publication is transferred to institution/company. 
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
  codedata: |
    All code and data are openly available. The ForC database and associated code is available via the ForC repository within the ForC-db organization on GitHub (https://github.com/forc-db/ForC), and the version used here (ForC v4.0) archived in Zenodo (DOI: TBD). The data and code associated with data submission to EFDB and preparation of this manuscript are available via the the IPCC-EFDB-integration repository within the ForC-db organization on GitHub  (https://github.com/forc-db/IPCC-EFDB-integration) and archived in Zenodo (DOI: 10.5281/zenodo.8021474). 
authorcontribution: |
  KAT and VH conceived and designed the project; VH wrote the scripts for database management, data submission to EFDB, and the analyses presented here; MW, TR, and RBM added and reviewed ForC data, BBL and SCP contributed large databases to ForC (EFDB and GROA, respectively); CP provided methodological expertise; KAT, VH, and MW prepared the first draft of the manuscript; all authors reviewed the results and approved the final version of the manuscript.
disclaimer: |
acknowledgements: |
  We gratefully acknowledge the substantial contributions of Valentyna Slivinska and Sandro Federici for collaboration on the conception, design, and technical review of this project.
  Thank you to all researchers who collected and published the data contained in ForC, and to all research assistants and collaborators who have contributed to building the database.
  Thank you to Avni Malhotra for helpful comments on an earlier draft of this manuscript.
  Funding for this study was provided by the Smithsonian (Forest Global Earth Observatory, Smithsonian Working Land and Seascapes); a Bezos Earth Fund grant to the Nature Conservancy, with a sub-grant to NZCBI; and the Institute for Global Environmental Strategies.
appendix: 
output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()

>>>>

bibliography: references.bib
running:
  title: Informing forest CO~2~ inventories with ForC
  author: Anderson-Teixeira et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed. 
# Note: additional copyright statements for affiliated software or data need to be placed in the data availability section. 
copyrightstatement: |
### The author's copyright for this publication is transferred to institution/company. 
### Note: unless stated otherwise, software and data affiliated with the manuscript are assumed to be published under the same licence as the article (currently Creative Commons 4.0)
availability:
  #  use this to add a statement when having only software code available
  #  use this to add a statement when having only data sets available
  #code: |
  #data: |
  codedata: |
    All code and data are openly available. The ForC database and associated code are available via the ForC repository within the ForC-db organization on GitHub (https://github.com/forc-db/ForC), and the version used here (ForC v4.0) is archived in Zenodo (DOI: TBD). The data and code associated with data submission to EFDB and preparation of this manuscript are available via the the IPCC-EFDB-integration repository within the ForC-db organization on GitHub  (https://github.com/forc-db/IPCC-EFDB-integration) and archived in Zenodo (DOI: 10.5281/zenodo.8021474). 
authorcontribution: |
  KAT and VH conceived and designed the project; VH wrote the scripts for database management, data submission to EFDB, and the analyses presented here; MW, TR, and RBM added and reviewed ForC data, BBL and SCP contributed large databases to ForC (EFDB and GROA, respectively); CP provided methodological expertise; KAT, VH, and MW prepared the first draft of the manuscript; all authors reviewed the results and approved the final version of the manuscript.
disclaimer: |
acknowledgements: |
  We gratefully acknowledge the substantial contributions of Valentyna Slivinska and Sandro Federici for collaboration on the conception, design, and technical review of this project.
  Thank you to all researchers who collected and published the data contained in ForC, and to all research assistants and collaborators who have contributed to building the database.
  Thank you to Avni Malhotra for helpful comments on an earlier draft of this manuscript.
  Funding for this study was provided by the Smithsonian (Forest Global Earth Observatory, Smithsonian Working Land and Seascapes); a Bezos Earth Fund grant to the Nature Conservancy, with a sub-grant to NZCBI; and the Institute for Global Environmental Strategies.
appendix: 
output:
  rticles::copernicus_article: default
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()

### 2023-06-09 doc/manuscript/ForC-EFDB-manuscript-for-ESSD.tex
refine data statement

\codedataavailability{All code and data are openly available. The ForC
database and associated code is available via the ForC repository within
the ForC-db organization on GitHub (https://github.com/forc-db/ForC),
and the version used here (ForC v4.0) archived in Zenodo (DOI: TBD). The
data and code associated with data submission to EFDB and preparation of
this manuscript are available via the the IPCC-EFDB-integration
repository within the ForC-db organization on GitHub
(https://github.com/forc-db/IPCC-EFDB-integration) and archived in
Zenodo (DOI:
10.5281/zenodo.8021474).} %% use this section when having data sets and software code available

>>>>

\codedataavailability{All code and data are openly available. The ForC
database and associated code are available via the ForC repository
within the ForC-db organization on GitHub
(https://github.com/forc-db/ForC), and the version used here (ForC v4.0)
is archived in Zenodo (DOI: TBD). The data and code associated with data
submission to EFDB and preparation of this manuscript are available via
the the IPCC-EFDB-integration repository within the ForC-db organization
on GitHub (https://github.com/forc-db/IPCC-EFDB-integration) and
archived in Zenodo (DOI:
10.5281/zenodo.8021474).} %% use this section when having data sets and software code available
